%-------------------------
% Resume in LaTeX
% Author : Patrick Iteghie
% Based off of : https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

% Core document setup
\usepackage[margin=0.5in]{geometry}
\usepackage[english]{babel}

% Colors and formatting
\usepackage[usenames,dvipsnames]{color}
\usepackage{titlesec}

% Lists and tables
\usepackage{enumitem}
\usepackage{tabularx}

% Links and PDF accessibility
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}

% Fonts and symbols
\usepackage{latexsym}
\usepackage{newtxtext,newtxmath}

% Headers and footers
\usepackage{fancyhdr}

% Page style and spacing
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlist{nosep,leftmargin=*}
\urlstyle{same}
\raggedbottom
\raggedright

% Section formatting
\titleformat{\section}{\fontsize{13pt}{15pt}\selectfont\scshape}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{2pt}{2pt}

% Ensure PDF is machine-readable/ATS parsable
\pdfgentounicode=1

% List commands
\newcommand{\resumeSubheadingListStart}{\begin{itemize}[leftmargin=0pt,label={},itemsep=2pt]}
\newcommand{\resumeSubheadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet,leftmargin=0.2in,itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
% Subheading: 1 line with bold, plain, and italic text
\newcommand{\resumeSubheadingOneLine}[3]{\item \textbf{#1} \textbar\ \textit{#2} \hfill\textbf{#3}}
% Subheading: 2 lines with bold and italic text
\newcommand{\resumeSubheadingTwoLine}[4]{\item \textbf{#1}\hfill\textbf{#2}\\
  \textit{#3}\hfill\textit{#4}}
\newcommand{\resumeItem}[1]{\item #1}

\begin{document}

%----------HEADING----------
\begin{center}
  \vspace*{-18pt}
  {\fontsize{15pt}{16pt}\selectfont\textbf{Patrick Iteghie}}\\
  \vspace{2pt}
  {\href{tel:+14692124668}{(469) 212-4668} \textbar\ \href{mailto:piteghie@outlook.com}{piteghie@outlook.com} \textbar\ 
  \href{https://www.linkedin.com/in/patrick-iteghie}{linkedin.com/in/patrick-iteghie} \textbar\ Gainesville, FL}
  \vspace{-2pt}
\end{center}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubheadingListStart
  \resumeSubheadingTwoLine{University of Florida}{May 2027}{Bachelor of Science in Computer Science and Mechanical Engineering}{GPA: 3.97}
  \item \textbf{Relevant Coursework:} Data Structures \& Algorithms, Algorithm Abstraction \& Design, Operating Systems, Database Systems, Programming Language Concepts, Computer Organization, Discrete Structures, Statistics, Linear Algebra, Numerical Methods
\resumeSubheadingListEnd

%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
\resumeSubheadingListStart
  \resumeSubheadingTwoLine{Expedia Group}{Seattle, WA}{Software Development Engineering Intern}{May 2025 -- Jul 2025}
  \resumeItemListStart
    \resumeItem{Engineered a scalable gRPC Configuration Management microservice in Kotlin and Spring Boot using hexagonal architecture, enabling a \$24M revenue opportunity through automated partner ad placement.}
    \resumeItem{Implemented CRUD APIs with MongoDB persistence and Protocol Buffers schemas for type-safe microservice communication.}
    \resumeItem{Integrated JWT-based SVID authentication and authorization, securing all workload communications.}
    \resumeItem{Achieved 90\%+ code coverage using JUnit 5 and MockK, maintaining code quality through Detekt, SonarQube, and JaCoCo.}
    \resumeItem{Conducted comprehensive UAT and integration testing to validate business logic and ensure service stability before deployment.}
    \resumeItem{Streamlined CI/CD pipeline using GitHub Actions, Docker containerization, and Spinnaker deployment with Datadog monitoring.}
  \resumeItemListEnd

  \resumeSubheadingTwoLine{Ultimate Kronos Group}{Weston, FL}{Software Engineering Intern}{May 2024 -- Aug 2024}
  \resumeItemListStart
    \resumeItem{Maintained and optimized the Pro Import Engine in C\#, processing millions of monthly transactions and integrating data across multiple business processes in an Agile environment.}
    \resumeItem{Accelerated end-to-end test suite execution by 49\% (32 to 16 hours) using Selenium and NUnit, preserving quality and coverage.}
    \resumeItem{Diagnosed and resolved critical CI pipeline test failures in TeamCity, addressing authorization and authentication issues to strengthen application security measures.}
    \resumeItem{Safeguarded against DDoS attacks by conducting comprehensive UI tests across multiple servers using Postman, TestRail, and Splunk, validating the Web Application Firewall performance.}
  \resumeItemListEnd

  \resumeSubheadingTwoLine{UF Digital Worlds Institute}{Gainesville, FL}{Research Assistant}{Jan 2023 -- May 2025}
  \resumeItemListStart
    \resumeItem{Co-authored "Investigating the Adoption and Integration of Game-Based Web Applications for Supplementing Literacy Instruction: A Longitudinal Case Study," submitted to Frontiers in Education.}
    \resumeItem{Collaborated with a multidisciplinary team to conduct nationwide survey research with 60+ K-2 teachers and tutors across 25 US states, examining adoption patterns and educational effectiveness of web-based literacy tools.}
    \resumeItem{Analyzed usage data across different instructional settings to identify patterns and guide future educational technology development.}
  \resumeItemListEnd

  \resumeSubheadingTwoLine{UF Design and Manufacturing Lab}{Gainesville, FL}{Teaching Assistant}{Jan 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Mentored 30+ engineering students through design processes, from concept planning to prototype development and iterative testing.}
    \resumeItem{Trained students on technical equipment operation, emphasizing safety protocols, standards, and troubleshooting methodologies.}
    \resumeItem{Guided students in technical documentation practices, emphasizing clarity, accuracy, and completeness in design reports.}
  \resumeItemListEnd
\resumeSubheadingListEnd

%-----------PROJECTS-----------
\section{\textbf{Projects}}
\resumeSubheadingListStart
  \resumeSubheadingOneLine{CURE Apps for Good}{JavaScript, Node.js, HTML, CSS, op.n framework (UF web platform)}{Jan 2023 -- May 2025}
  \resumeItemListStart
    \resumeItem{Developed cross-platform literacy games for K-2 students with 100,000+ daily active users, implementing responsive web design for compatibility across desktop, tablet, and mobile devices.}
    \resumeItem{Designed an automated Node.js pipeline to streamline digitization of 100+ vocabulary lessons, eliminating manual conversion.}
    \resumeItem{Managed development using GitHub and Agile methodology, coordinating weekly sprint cycles to deliver 8 educational games.}
  \resumeItemListEnd

  \resumeSubheadingOneLine{Cinema Compass}{Python, NumPy, Pandas, NetworkX, Streamlit}{Jul 2023 -- Aug 2023}
  \resumeItemListStart
    \resumeItem{Built a graph-based actor discovery web application processing 20,000+ IMDb entries using BFS/DFS algorithms with $<\!0.1$s search performance, winning first place in class competition.}
    \resumeItem{Created an interactive network visualization with NetworkX and Pyvis, deployed via Streamlit for cross-platform web access.}
    \resumeItem{Established a data processing pipeline using NumPy and Pandas to manipulate actor records, integrating Cinemagoer API for real-time movie information retrieval.}
  \resumeItemListEnd
\resumeSubheadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{\textbf{Technical Skills}}
\resumeSubheadingListStart
  \item{\textbf{Languages}: C++, Java, Python, JavaScript, C\#, Kotlin, MATLAB}
  \item{\textbf{Technologies \& DevOps}: Node.js, MongoDB, SQL, Docker, gRPC, REST, Protocol Buffers, Postman, Git, Bitbucket, Jira, TeamCity, GitHub Actions, Spinnaker, Maven, Artifactory, TestRail, Splunk, Datadog, JWT, SVID}
  \item{\textbf{Frameworks \& Libraries}: Spring Boot, .NET, React, JUnit, NUnit, Selenium, MockK, JaCoCo, Detekt, SonarQube, NumPy, Pandas}
\resumeSubheadingListEnd

\end{document}
